Narrative

### 2023-05-23 manuscript/manuscript.qmd
result: copyedits

_Figure 1._ EXPLANATION. Code to reproduce figure: LINK.

@@

For all heterogeneity levels in Figure 1 above zero we see an overall underestimate of heterogeneity due to unreliability in primary studies. This negative bias can be relatively severe, is worse with lower average reliability, and is worse in an absolute sense but better in a relative sense as heterogeneity increases. For example, for $\bar{R} = 0.8$, $\mu = 0.2$, $\tau = 0.1$, the bias is XX (XX%) for Pearson's r, for $\bar{R} = 0.8$, $\mu = 0.2$, $\tau = 0.15$ the bias is XX (XX%), and for $\bar{R} = 0.8$, $\mu = 0.2$, $\tau = 0.2$ the bias is XX (XX%).

@@

>>>>

@@

For all heterogeneity levels in Figure 1 above zero we see an overall underestimate of heterogeneity due to unreliability in primary studies. This negative bias can be relatively severe, is worse with lower effect size and lower average reliability, and worsens in an absolute sense but improves in a relative sense as heterogeneity increases. For example, for $\bar{R} = 0.8$, $\mu = 0.2$, $\tau = 0.1$, the bias is XX (XX%) for Pearson's r, for $\bar{R} = 0.8$, $\mu = 0.2$, $\tau = 0.15$ the bias is XX (XX%), and for $\bar{R} = 0.8$, $\mu = 0.2$, $\tau = 0.2$ the bias is XX (XX%).

@@

_Figure 3._ EXPLANATION. Code to reproduce figure: LINK.
